### 2020-06-26 2020/WCGO_MCO_OptimizationLetters/2020_WCGO_MCO.tex
fix some obvious typos

This approach is also widely known as the $\varepsilon$-constraint method (or the method of successive concessions) \cite{c39,c40,c41,c42}. The choice of feasible concessions $\delta_i$, $1 \leq i \leq s$ in the computational scheme (\ref{eq:9}) allows obtaining any efficient decision $\widetilde{y}^* \in P_{lex}(f,D)$ and takes into account the peculiarities of the MCOlex problem. At the same time, this approach makes it necessary, at each stage of the scheme (\ref{eq:9}), to solve more complex global optimization problems with nonlinear constraints.

@@

The first trial is carried out at an arbitrary internal point $x^1\in(0,1)$. The choice of the point $x^{k+1}$, $k \geq 1$ of any next trial is determined by the following rules

@@

\textit{Rule 3.} Execute a new trial at the point $x^{k+1} \in (x_{t-1},x_t)$, determined in accordance with the expression
\begin{equation}\label{eq:27}
x^{k+1} = \mathcal{X}(x_{t-1},x_t)
\end{equation}
where the expression $\mathcal{X}(x_{t-1},x_t)$ is also set by AGCS.

Iterations of the algorithm are terminated if the stop criterion is satisfied

\begin{equation}\label{eq:28}
\rho_t\leq \varepsilon,
\end{equation}
where $t$ from (\ref{eq:26}), $\rho_t = \sqrt[N]{x_t-x_{t-1}}$ and $\varepsilon > 0$ is the given accuracy.

@@

\begin{theorem}
If the AGCS algorithm is used to solve the problem (\ref{eq:16}), and the following conditions are satisfied:
\begin{enumerate}
	\item the functions $g_j$, $1 \leq j \leq m+1$, $[0,1]$ satisfy the H\"older condition of (\ref{eq:13}) with the constants $H_j$, $1 \leq j \leq m+1$,
	\item for the values $H^k_\nu$ from (\ref{eq:24}), starting from a certain step, the inequalities are valid\footnote{The values $r_{\nu} > 1$, $1 \leq \nu \leq m+1$,are the AGCS reliability parameters used for computing the interval characteristics in (\ref{eq:25}).}
\begin{equation} \label{eq:29}
r_\nu H^k_\nu > 2H_\nu, r_\nu > 1, 1 \leq \nu \leq m+1,
\end{equation}
\end{enumerate}
then the set of limit points of the sequence $\{x^k\}$ generated by the algorithm coincides with the set of global minimum points of the problem (\ref{eq:16}) with $\varepsilon=0$ in the stopping criterion (\ref{eq:28}).
\end{theorem}

@@

With a complete scheme for calculating criteria values, i.e. when at the iteration points $x_i$, $1 \leq i \leq k$ the values of all criteria $f_j(x_i)$, $1 \leq j \leq s$, $1 \leq i \leq k$, are calculated, the effect of using the search information $A_k$ can be even more significant. In this case, the search information can also be used when changing the values of the concessions $\delta_j$, $1 \leq j < s$ and thus, the solution of the next problem from the $\mathbb{P}_t$ family (\ref{eq:10}) can be carried out repeatedly using the results of all previously performed calculations. The results of numerical experiments (see Section \ref{sec:5}), demonstrate that the volume of computations performed, based on reusing search information, can significantly decrease.

@@

\bibitem{c55} Cust\'odio, A.L., Aguilar, J.F. Madeira, Ismael Vaz, Lu\'ls N. Vicente: Direct Multisearch for Multiobjective Optimization. IAM Journal on Optimization 21(3). pp. 1109-1140 (2011)

@@

\bibitem{c59} Lai, L. , Fiaschi, L. , Cococcioni, M.: Solving Mixed Pareto-Lexicographic Multi-Objective Optimization Problems: The Case of Priority Chains, Swarm and Evolutionary Computation, 55. pp. 100687 (2020) DOI: 10.1016/j.swevo.2020.100687

>>>>

This approach is also widely known as the $\varepsilon$-constraint method (or the method of successive concessions) \cite{c39,c40,c41,c42}. The choice of feasible concessions $\delta_i$, $1 \leq i \leq s$, in the computational scheme (\ref{eq:9}) allows obtaining any efficient decision $\widetilde{y}^* \in P_{lex}(f,D)$ and takes into account the peculiarities of the MCOlex problem. At the same time, this approach makes it necessary, at each stage of the scheme (\ref{eq:9}), to solve more complex global optimization problems with nonlinear constraints.

@@

The first trial is carried out at an arbitrary internal point $x^1\in(0,1)$. The choice of the point $x^{k+1}$, $k \geq 1$, of any next trial is determined by the following rules.

@@

\textit{Rule 3.} Execute a new trial at the point $x^{k+1} \in (x_{t-1},x_t)$, determined in accordance with the expression
\begin{equation}\label{eq:27}
x^{k+1} = \mathcal{X}(x_{t-1},x_t),
\end{equation}
where the expression $\mathcal{X}(x_{t-1},x_t)$ is also set by AGCS.

Iterations of the algorithm are terminated if the stop criterion is satisfied
\begin{equation}\label{eq:28}
\rho_t\leq \varepsilon,
\end{equation}
where $t$ from (\ref{eq:26}), $\rho_t = \sqrt[N]{x_t-x_{t-1}}$ and $\varepsilon > 0$ is the given accuracy.

@@

\begin{theorem}
If the AGCS algorithm is used to solve the problem (\ref{eq:16}), and the following conditions are satisfied:
\begin{enumerate}
	\item the functions $g_j(x)$, $1 \leq j \leq m+1$, $x\in[0,1]$, satisfy the H\"older condition (\ref{eq:13}) with the constants $H_j$, $1 \leq j \leq m+1$,
	\item for the values $H^k_\nu$ from (\ref{eq:24}), starting from a certain step, the inequalities are valid\footnote{The values $r_{\nu} > 1$, $1 \leq \nu \leq m+1$, are the AGCS reliability parameters used for computing the interval characteristics in (\ref{eq:25}).}
\begin{equation} \label{eq:29}
r_\nu H^k_\nu > 2H_\nu, r_\nu > 1, 1 \leq \nu \leq m+1,
\end{equation}
\end{enumerate}
then the set of limit points of the sequence $\{x^k\}$ generated by the algorithm coincides with the set of global minimum points of the problem (\ref{eq:16}) with $\varepsilon=0$ in the stopping criterion (\ref{eq:28}).
\end{theorem}

@@

With a complete scheme for calculating criteria values, i.e. when at the iteration points $x_i$, $1 \leq i \leq k$, the values of all criteria $f_j(x_i)$, $1 \leq j \leq s$, $1 \leq i \leq k$, are calculated, the effect of using the search information $A_k$ can be even more significant. In this case, the search information can also be used when changing the values of the concessions $\delta_j$, $1 \leq j < s$, and thus, the solution of the next problem from the $\mathbb{P}_t$ family (\ref{eq:10}) can be carried out repeatedly using the results of all previously performed calculations. The results of numerical experiments (see Section \ref{sec:5}), demonstrate that the volume of computations performed, based on reusing search information, can significantly decrease.

@@

\bibitem{c55} Cust\'odio, A.L., Aguilar, J.F. Madeira, Ismael Vaz, Lu\'ls N. Vicente: Direct Multisearch for Multiobjective Optimization. SIAM J. Optim. 21(3). pp. 1109--1140 (2011)

@@

\bibitem{c59} Lai, L., Fiaschi, L., Cococcioni, M.: Solving Mixed Pareto-Lexicographic Multi-Objective Optimization Problems: The Case of Priority Chains, Swarm and Evolutionary Computation, 55. pp. 100687 (2020) DOI: 10.1016/j.swevo.2020.100687
